A Possibilistic Valid-time Model

### 2012-03-29 ipmu2012/introduction.tex
Modifications sugested by reviewers + new bibliography.

One issue in these attempts at temporal modelling is off course the inherent complexities of the concept of time. Another is the possible inherent imperfections in the description of notions of time. The description of the temporal notion in a sentence like `The Alhambra, which I can see from my room, is a few hundred years old.' contains imperfection caused by the vagueness of the used expression. The description of the temporal notion in a sentence like `The Alhambra was finished somewhere between 1301 A.D. and 1400 A.D.' contains imperfection caused by the uncertainty in the used expression about the exact finishing day of the building. Though precise boundaries are given, the exact day on which the building was finished is unknown. The transition between temporal granularities~\cite{Lin97} is also considered as a source of imprecision in temporal modelling and some proposals consider granularity as the base of the temporal model~\cite{Cru97}.

@@

To allow information systems to cope with these imperfections, many approaches adopt fuzzy sets for the representation of temporal information~\cite{Billiet:Pons:Matthe:DeTre:Pons:2011:BipolarFuzzy},\cite{Dubois:jucs_9_9:fuzziness_and_uncertainty_in}. The temporal relations studied by Allen were recently fuzzified by several authors~\cite{ohlbach04},\cite{schockaert08}.

Next to the issues in temporal modelling, the inclusion of time in a relational database system leads to several more practical problems, as the modelling of the temporal aspects of a time-variant object has an impact on the database consistency. Different models have been proposed \cite{Jensen91},\cite{Snodgrass84},\cite{Nascimento95} that consider time as a crisp notion. In some specific works, authors consider the necessity of allowing imprecision in temporal models~\cite{Cru97},\cite{Garrido2009}.

>>>>

One issue in these attempts at temporal modelling is of course the inherent complexities of the concept of time. Another is the possible inherent imperfections in the description of notions of time. The description of the temporal notion in a sentence like `The Alhambra, which I can see from my room, is a few hundred years old.' contains imperfection caused by the vagueness of the used expression. The description of the temporal notion in a sentence like `The Alhambra was finished somewhere between 1301 A.D. and 1400 A.D.' contains imperfection caused by the imprecision in the used expression about the exact finishing day of the building. Though precise boundaries are given, the exact day on which the building was finished is unknown. An example of uncertainty is given by the following sentence: `I believe that the Alhambra was finished in 1300 A.D.'

The transition between temporal granularities~\cite{Lin97} is also considered as a source of imprecision in temporal modelling and some proposals consider granularity as the base of the temporal model~\cite{Cru97}.

@@

To allow information systems to cope with these imperfections, there are some approaches that work with probability~\cite{Dekhtyar2001},~\cite{Parisi2010} whereas some other approaches adopt fuzzy sets for the representation of temporal information~\cite{Billiet:Pons:Matthe:DeTre:Pons:2011:BipolarFuzzy},\cite{Dubois:jucs_9_9:fuzziness_and_uncertainty_in}. The temporal relations studied by Allen were recently fuzzified by several authors~\cite{ohlbach04},\cite{schockaert08}.

Next to the issues in temporal modelling, the inclusion of time in a relational database system leads to several more practical problems, as the modelling of the temporal aspects of a time-variant object has an impact on the database consistency. Different models have been proposed \cite{Jensen91},\cite{Snodgrass84},\cite{Nascimento95} that consider time as a crisp notion. Some of these models uses TSQL~\cite{Jensen1995} (a temporal extension to SQL) as query language. In some specific works, authors consider the necessity of allowing imprecision in temporal models~\cite{Cru97},\cite{Garrido2009}.
